---
title: "Piloting Graph Learning in Children: CNL004 to CNL006"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
CNL006 hsa the updated version of the task, withtapping on the monsters to advance, tap as quickly as you can, the tap makes a sound, and string all assessments together rather than opening each separately. Also eliminated catch trials in the OMOT.

## CNL004
```{r}
suppressPackageStartupMessages(library(summarytools, quietly = TRUE))
suppressPackageStartupMessages(library(dplyr, quietly = TRUE))
logdir='/Users/utooley/Dropbox/projects/in_progress/network_learning/code/netlearn_kids_v1/logs/'
datadir='~/Dropbox/projects/in_progress/network_learning/code/netlearn_kids_v1/subjData/'
exposureData <- read.delim(paste0(logdir, "CNL004/CNL004_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "CNL004/seqcmpl/CNL004_log_seqcmpl.csv"))
omotData<- read.csv(paste0(datadir, "CNL004/OMOT/CNL004_log_omot.csv"))
#dyadicData<- read.csv(paste0(datadir, "CNL002/dyad_choice/CNL002_log_dyad_choice.csv"))
seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, labels=c("Incorrect", "Correct"))
exposureData$rt <- as.numeric(as.character(exposureData$rt))
```

### Exposure Data

```{r}
summary(exposureData$rt)
```
Wow, much faster!

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt, main="Sample Kid")
cor.test(exposureData$TrialNumber, exposureData$rt)
```
It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
No, not really.

**How long does it take with 150 nodes (of which 4 are practice trials)?**
```{r}
max(exposureData$onset)/60
```
## Sequence Completion Task

How many are correct? 75%.
```{r}
table(seqcmplData$correct)
```

## Odd Man Out Task-Did not do
```{r}
summary(omotData$correct)
```
On average, 20% correct on OMOT.

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
The 'correct' answer for catch trials is the node that is 2 edges away rather than one edge away. 72% is still above chance on the conservative trials!

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Average RT is highest in catch trials, lowest in conservative trials, as we would expect. Median RT is highest in non-conservative trials and lowest in conservative trials, again as we would expect.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```

### Conclusions

75% on sequence completion, but not successful at OMOT, on average 20%, which is below chance. No trial type was above chance.
Took 5-6 minutes with 150 noges.

##CNL005

This participant was really tired by the end, though she did dyadic choice, she just tapped randomly, alternating between yes and no, so did not examine.

```{r}
exposureData <- read.delim(paste0(logdir, "CNL005/CNL005_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "CNL005/seqcmpl/CNL005_log_seqcmpl.csv"))
#omotData<- read.csv(paste0(datadir, "CNL005/OMOT/CNL005_log_omot.csv"))
#seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(1,0), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```

## Check exposure data quality

```{r}
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt)
cor.test(exposureData$TrialNumber, exposureData$rt)
```
It goes down (not surprisingly)!

**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Not really.

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
## Sequence Completion Task

```{r}
summary(seqcmplData$correct)
```
How many are correct? 37%
```{r}
table(seqcmplData$correct)
```
### Conclusions

Participant did not seem to want to try by the time we got to the assessments, it was still too long, perhaps? Sequence completion at 37% accuracy, below chance. Also did not incentivize right, maybe?
Exposure was 7.3 min.

## CNL006

Here made the change for tapping on the monsters to advance, tap as quickly as you can, the tap makes a sound, and string all assessments together rather than opening each separately. Also removed catch trials from the OMOT.

```{r}
exposureData <- read.delim(paste0(logdir, "CNL006/CNL006_log_run1.csv"))
seqcmplData <- read.csv(paste0(datadir, "CNL006/seqcmpl/CNL006_log_seqcmpl.csv"))
omotData<- read.csv(paste0(datadir, "CNL006/OMOT/CNL006_log_omot.csv"))
#seqcmplData$correct <- factor(seqcmplData$correct, ordered=TRUE, levels=c(1,0), labels=c("Incorrect", "Correct"))
#omotData$correct <- factor(omotData$correct, ordered=TRUE, labels=c("Incorrect", "Correct")) #commented out because if make them factors then can't do proportion calculations on them.
```

## Exposure Data

```{r}
summary(exposureData$rt)
```

**Does RT go down or up as the task goes on?**

```{r}
plot(exposureData$TrialNumber, exposureData$rt)
cor.test(exposureData$TrialNumber, exposureData$rt)
```
It goes down (not surprisingly)!
**Is RT longer after transition nodes?**
```{r}
exposureData$transition_node <- ifelse((exposureData$node1==4 & exposureData$node2 ==5) |(exposureData$node1 ==5 & exposureData$node2 ==4), 1, 0)
exposureData$transition_node <- factor(exposureData$transition_node, labels=c("No", "Yes"))
exposureData %>%  group_by(transition_node) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
No, it's not.

**How long does it take with 150 nodes?**
```{r}
max(exposureData$onset)/60
```
## Sequence Completion Task
Data quality
```{r}
summary(seqcmplData$correct)
```
How many are correct? 63%.
```{r}
table(seqcmplData$correct)
```
## Odd Man Out Task
```{r}
summary(omotData$correct)
```
47% correct on OMOT.

Does average number correct differ by trial type?
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_correct=mean(correct))
```
Yes-above chance on conservative trials, but at chance on non-conservative trials.

**Does RT differ by trial type?**
```{r}
omotData %>% group_by(trial_type) %>% summarise(avg_rt=mean(rt), med_rt=median(rt), std_dev=sd(rt), n_trials=n())
```
Higher in non-conservative trials, as expected.

**Does RT differ by sequence-longer later in the sequence, or shorter?**
```{r}
cor.test(omotData$TrialNumber, omotData$rt)
```
Not strongly so.

### Conclusions

Seems like he understood--63% accuracy on sequence completion and 47% accuracy on the OMOT, which is driven by accuracy on conservative trials (60%) over non-conservative trials.
RT on OMOT looks as we might expect, lower for conservative trials than non-conservative.
Took 8.5 min with 150 nodes.
RT is not longer on transition nodes (4 to 5 or 5 to 4).